\LARGE \bf Simultaneous Hand-Eye and Robot-World Calibration by Solving the AX=YB Problem without Correspondence*

### 2015-11-22 Final Submission/root1.tex
Final Submission

Any rigid body transformation matrix can be viewed as a group element of $SE(3)$ :
\begin{equation}\label{equ0}
    H(R,t)=\left(
             \begin{array}{cc}
               R & t \\
               0^{T} & 1 \\
             \end{array}
           \right) \in SE(3), \; \; R \in SO(3)
\end{equation}
where $SO(3)$ denotes the special orthogonal group, $t \in \mathbb{R}^3 $ is a translational vector,
 $T$ denotes the transpose of a vector or matrix, and $H$ is the symbol for an element of $SE(3)$
 (which is a six-dimensional Lie group) represented as a $4\times 4$ homogeneous transformation matrix.
 The identity element of $SE(3)$ is then the $4\times 4$ identity matrix, $I$.

@@

\begin{equation}\label{equ2}
\delta{(H)}=
\left\{
\begin{array}{lll}
+\infty& {\rm if} & H=I \\
0& {\rm if} & H \neq I,
\end{array}
\right.
\end{equation}
and also satisfies the identity constraint

@@

\begin{IEEEeqnarray}{l}\label{equ11}
\int_{SE(3)} \log(M^{-1}H)f(H)dH = \mathbb{O}  \IEEEyessubnumber
\\*
\Sigma = \int_{SE(3)} \log^{\vee}(M^{-1}H)[\log^{\vee}(M^{-1}H)]^{T}f(H)dH \; \; \; \; \;
\IEEEyessubnumber
\end{IEEEeqnarray}
where the explicit expression of the matrix logarithm $\log(H)$ along with its vectorized form $\log^{\vee}(H)$ are given in \cite{MLK} as

@@

\begin{IEEEeqnarray}{l}\label{equ12}
\sum_{i=1}^{n}\log(M_A^{-1}A_i) = \mathbb{O} \IEEEyessubnumber
\\*
\Sigma = \sum_{i=1}^{n}\log^{\vee}(M_A^{-1}A_i)[\log^{\vee}(M_A^{-1}A_i)]^{T}. \IEEEyessubnumber
\end{IEEEeqnarray}

@@

$$Ad(H)=\left(
               \begin{array}{cc}
                 R & O \\
                 \hat{t}R & R \\
               \end{array}
             \right).$$
Here the ``hat'' notation when applied to the three-dimensional vector $t$ gives
\begin{equation}
\hat{t}
=
\left(
\begin{array}{ccc}
   0 & -t_3 &  t_2 \\
 t_3 &    0 & -t_1 \\
-t_2 & -t_1 &    0
\end{array}
\right)
\end{equation}

Because $X$ and $Y$ are constant, their corresponding PDF will be $\delta_{X}(g)$ and $\delta_{Y}(g)$, of which the mean and covariance are $M_{X} = X$, $\Sigma_{X} = \mathbb{O}_{6 \times 6}$ and $M_{Y} = Y$, $\Sigma_{Y} = \mathbb{O}_{6 \times 6}$, respectively. Therefore, the following equations can be obtained using Eq.~(\ref{equ14}):

@@

Starting with Eq.(\ref{equ9}), performing a convolution on both of the left sides of the equation with
$\delta_{Y^{-1}}(H)$, and using the associativity of convolution, we will have:
\begin{equation} 
(\delta_{Y^{-1}} * f_A * \delta_X)(H) = f_B(H).
\label{equ18new}
\end{equation}
Use the definition of mean as in Eq.~(\ref{equ11}) along with Eq.~(\ref{equ18new}), we have 
$$ \int_{SE(3)} \log({M}_{B}^{-1} H) f_B(H) dH = $$
$$ \int_{SE(3)} \log({M}_{B}^{-1} H) (\delta_{X^{-1}} * f_A * \delta_{X})(H) dH = $$
\begin{equation}
\int_{SE(3)} \log({M}_{B}^{-1} H) f_A({Y} H {X}^{-1}) dH = \mathbb{O}.
\label{equ19new}
\end{equation}
Change the variable as $K = {Y} H {X}^{-1}$ and use the invariance of integration \cite{chirikjian2011stochastic}, then Eq.~(\ref{equ19new}) becomes:
\begin{equation}
\int_{SE(3)} \log({M}_{B}^{-1} Y^{-1} K X) f_A(K) dK = \mathbb{O}. 
\label{equ20new}
\end{equation}
which falls into the form of the mean definition of $\{A_i\}$.
If we further multiply $X$ and $X^{-1}$ on the left and right of both sides of Eq.~(\ref{equ20new}), then $X[\log({M}_{B}^{-1} Y^{-1} K X)]X^{-1} = \log(M_{A}^{-1}K)$.
Knowing that $X[\log({M}_{B}^{-1} Y^{-1} K X)]X^{-1} = \log(X {M}_{B}^{-1} Y^{-1} K)$, and we have 
$X {M}_{B}^{-1} Y^{-1} = M_{A}^{-1}$ which is equivalent to Eq.~(\ref{equ15a}). Eq.(\ref{equ15b}) follows from \cite{wang2008nonparametric} because the F(A,B) term has products of covariances of the functions being convolved, and delta functions have zero covariance so the F term is zero.

>>>>

Any rigid body transformation matrix can be viewed as a group element of $SE(3)$ :
\begin{equation}\label{equ0}
    H(R,t)=\left(
             \begin{array}{cc}
               R & t \\
               0^{T} & 1 \\
             \end{array}
           \right) \in SE(3), \; \; R \in SO(3)
\end{equation}
where $SO(3)$ denotes the special orthogonal group, $t \in \mathbb{R}^3 $ is a translational vector,
 $T$ denotes the transpose of a vector or matrix, and $H$ is the symbol for an element of $SE(3)$
 (which is a six-dimensional Lie group) represented as a $4\times 4$ homogeneous transformation matrix.
 The identity element of $SE(3)$ is then the $4\times 4$ identity matrix, $I_4$.

@@

\begin{equation}\label{equ2}
\delta{(H)}=
\left\{
\begin{array}{lll}
+\infty& {\rm if} & H=I_4 \\
0& {\rm if} & H \neq I_4,
\end{array}
\right.
\end{equation}
and also satisfies the identity constraint

@@

\begin{IEEEeqnarray}{l}\label{equ11}
\int_{SE(3)} \log(M^{-1}H)f(H)dH = \mathbb{O}_4  \IEEEyessubnumber
\\*
\Sigma = \int_{SE(3)} \log^{\vee}(M^{-1}H)[\log^{\vee}(M^{-1}H)]^{T}f(H)dH \; \; \; \; \;
\IEEEyessubnumber
\end{IEEEeqnarray}
where the explicit expression of the matrix logarithm $\log(H)$ along with its vectorized form $\log^{\vee}(H)$ are given in \cite{MLK} as

@@

\begin{IEEEeqnarray}{l}\label{equ12}
\sum_{i=1}^{n}\log(M_A^{-1}A_i) = \mathbb{O}_4 \IEEEyessubnumber
\\*
\Sigma = \sum_{i=1}^{n}\log^{\vee}(M_A^{-1}A_i)[\log^{\vee}(M_A^{-1}A_i)]^{T}. \IEEEyessubnumber
\end{IEEEeqnarray}

@@

$$Ad(H)=\left(
               \begin{array}{cc}
                 R & \mathbb{O}_4 \\
                 \hat{t}R & R \\
               \end{array}
             \right).$$
Here the ``hat'' notation when applied to the three-dimensional vector $t$ gives
\begin{equation}
\hat{t}
=
\left(
\begin{array}{ccc}
   0 & -t_3 &  t_2 \\
 t_3 &    0 & -t_1 \\
-t_2 & -t_1 &    0
\end{array}
\right)
\end{equation}

Because $X$ and $Y$ are constant, their corresponding PDF will be $\delta_{X}(g)$ and $\delta_{Y}(g)$, of which the mean and covariance are $M_{X} = X$, $\Sigma_{X} = \mathbb{O}_{6 }$ and $M_{Y} = Y$, $\Sigma_{Y} = \mathbb{O}_{6}$, respectively. Therefore, the following equations can be obtained using Eq.~(\ref{equ14}):

@@

Starting with Eq.(\ref{equ9}), performing a convolution on both of the left sides of the equation with
$\delta_{Y^{-1}}(H)$, and using the associativity of convolution, we will have:
\begin{equation} 
(\delta_{Y^{-1}} * f_A * \delta_X)(H) = f_B(H).
\label{equ18new}
\end{equation}
Use the definition of mean as in Eq.~(\ref{equ11}) along with Eq.~(\ref{equ18new}), we have 
$$ \int_{SE(3)} \log({M}_{B}^{-1} H) f_B(H) dH = $$
$$ \int_{SE(3)} \log({M}_{B}^{-1} H) (\delta_{X^{-1}} * f_A * \delta_{X})(H) dH = $$
\begin{equation}
\int_{SE(3)} \log({M}_{B}^{-1} H) f_A({Y} H {X}^{-1}) dH = \mathbb{O}_4.
\label{equ19new}
\end{equation}
Change the variable as $K = {Y} H {X}^{-1}$ and use the invariance of integration \cite{chirikjian2011stochastic}, then Eq.~(\ref{equ19new}) becomes:
\begin{equation}
\int_{SE(3)} \log({M}_{B}^{-1} Y^{-1} K X) f_A(K) dK = \mathbb{O}_4. 
\label{equ20new}
\end{equation}
which falls into the form of the mean definition of $\{A_i\}$.
If we further multiply $X$ and $X^{-1}$ on the left and right of both sides of Eq.~(\ref{equ20new}), then $X[\log({M}_{B}^{-1} Y^{-1} K X)]X^{-1} = \log(M_{A}^{-1}K)$.
Knowing that $X[\log({M}_{B}^{-1} Y^{-1} K X)]X^{-1} = \log(X {M}_{B}^{-1} Y^{-1} K)$, and we have 
$X {M}_{B}^{-1} Y^{-1} = M_{A}^{-1}$ which is equivalent to Eq.~(\ref{equ15a}). Eq.(\ref{equ15b}) follows from \cite{wang2008nonparametric} because the $F(A,B)$ term as defined in \cite{wang2008nonparametric} has products of covariances of the functions being convolved, and delta functions have zero covariance so the $F(A,B)$ term is zero, which results in Eq.~(\ref{equ15b}).
